SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-06 docs/questioning.tex
some additions / fixes

	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc s}) & {\sc dom}-based {\sc xss} \\

@@

However, in this case of mechanisms that deal
with JavaScript-driven {\sc xss} attacks
we observe that attack detection may take place
either on the server-side or on the client-side.

>>>>

	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\

@@

However, in the case of frameworks that deal
with JavaScript-driven {\sc xss} attacks
we observe that attack detection may take place
either on the server-side or on the client-side.
In the first case, a proxy is placed on the server
to examine the server's responses before they
reach the user's web browser. In the second
case a modified browser or a library that
is securely downloaded from the server,
checks the responses for potential attacks.
Our findings indicate that the tendency so far,
is to create frameworks that perform detection
on the client side. In particular, 11 out of
19 frameworks ({\bf 57,8\%}) detect JavaScript-driven
{\sc xss} attacks at the client's side.
Note that the majority of the mechanisms that
detect such attacks on the server-side, can also
detect
